\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{Problem Statement and Goals\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Jan 26, 2023 & Runze Zhao & First draft\\
\bottomrule
\end{tabularx}
\end{table}

\section{Problem Statement}

\subsection{Problem}
Real estate market has always been an important factor to the economy. During the ongoing recession period, people pay more and more attention to the change of housing market; Especially for the ones who are going to sell or buy a house. The price tags on the properties are commonly based on the nearby sold houses. This approach lacks of scientific measurements. Sellers are buyers are very limited to the tools or models that could predict the price in the near future. The demand for such tool is growing rapidly. There are many regression techniques used in machine learning could be used to predict future house price based on the historical data sets. Each one of them could output different predictions, which can be used by related stakeholders when they sell or buy a house.

\subsection{Inputs and Outputs}
\subsubsection{Inputs}
\begin{itemize}
    \item Data sets of historical sold houses
\end{itemize}

\subsubsection{Outputs}
\begin{itemize}
    \item Prediction of multiple linear regression model
    \item Prediction of LASSO regression model
    \item Prediction of gradient boosting regression model
\end{itemize}

\subsection{Stakeholders}
\begin{itemize}
    \item Real estate brokers and agents
    \item House buyers and sellers
\end{itemize}

\subsection{Environment}
The software can be deployed on any OS

\section{Goals}
The software will give people better prediction of house prices in the near future

\section{Stretch Goals}
Find which regression model has the most accurate prediction
\end{document}
